Data Science Final Project

### 2022-05-31 paper-writeup.Rmd
update paper

As usual, Lasso assumes that the response variable $y$ follows a linear relation with the predictor variables $y = X\beta + \epsilon$, where $\epsilon$ is Normally distributed with mean 0.

@@

## Interprtation of coefficients

# Discussion and Limitations

Assumptions possibly not met, curse of dimensionality, did not incorporate census data

>>>>

As usual, Lasso assumes that the response variable $y$ follows a linear relation with the predictor variables $y = X\beta + \epsilon$, where $\epsilon$ is Normally distributed with mean 0. Also, since all predictor variables are assumed to be quantitative, we transformed categorical variables such as `nbhd` into dummy variables.

@@

## Interpretation of coefficients

Inspecting the coefficients chosen by the Lasso model, we found that among the total 61 variables (most of them dummy variables), only 41 of them have nonzero coefficients. The largest coefficients (in terms of absolute value) are `yearSold` (412690), followed by `fullBath` (232332) and `halfBath` (57121). This means that on average, house prices increase each year by around 0.4 million dollars, and each additional full bathroom increases house prices by around 0.23 million dollars.

```{r, warning = FALSE, echo = FALSE, results = "hide"}
x = as.matrix(select(filter(dummySplit, id != 0), -id))
xTest = as.matrix(select(filter(dummySplit, id == 0), -id))
y = filter(houseSplit, id != 0)$soldPrice
yTest = filter(houseSplit, id == 0)$soldPrice
bestLambda <- 6309
bestModel <- glmnet(x, y, alpha = 1, lambda = bestLambda)
bestModel$beta
```

# 3. Discussion and Limitations

Assumptions are possibly not met, curse of dimensionality, did not incorporate census data
